Appendix 4: Dynamic species distribution model comparison between INLA, inlabru, and sdmTMB

### 2022-01-08 doc/appendix-binomial-inla.Rmd
more minor edits

We can make similar predictions with inlabru using only a few additional steps: we must recreate `i_year`, create a `SpatialPixelsDataFrame` class data frame, and specify in `formula` to include both the random field (`f`), the factors (`fac`), and the appropriate inverse-link transformation:

@@

Similar predictions are more complicated to extract from INLA, but are easy to plot for the original sample locations.

>>>>

We can get similar predictions with inlabru using only a few additional steps: we must recreate `i_year`, create a `SpatialPixelsDataFrame` class data frame, and specify in `formula` to include both the random field (`f`), the factors (`fac`), and the appropriate inverse-link transformation:

@@

Equivalent predictions are more complicated to extract from INLA, but are easy to plot for the original sample locations.
